Explore Local Memory Design for Building Hypervisor on Resource Disaggregated Architecture

### 2019-11-04 paper.tex
Add memory hierarchy figure and fixup figure setting.

\begin{figure*}[h!]
     \centering
     \captionsetup[subfigure]{position=b}
     \begin{subfigure}[b]{0.28\textwidth}
         \includegraphics[height=.2\textheight]{figures/monolithic.png}
         \caption{Monolithic architecture, hardware components are bounded within a machine.}
         \label{fig:monolithic architecture}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.68\textwidth}
         \includegraphics[height=.2\textheight]{figures/disaggregated.png}
         \caption{Disaggregated architecture, hardware components are separate: there are CPU-blade, memory-blade, storage-blade. We also assume there is local memory located with CPU}
         \label{fig:disaggregated architecture}
     \end{subfigure}
     \caption{Monolithic architecture and disaggregated architecture.}
     \label{fig:architecture}
\end{figure*}

@@

@@

% Figure of local memory architecture
\begin{figure*}[h!]
     \centering
     \captionsetup[subfigure]{position=b}
     \begin{subfigure}[b]{\textwidth}
         \includegraphics[height=.05\textheight,width=\linewidth]{figures/memory_region.png}
         \caption{Separate physical main memory into local (slash-filled) and remote memory resgions.}
         \label{fig:local memory regions}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{\textwidth}
         \includegraphics[height=.1\textheight,width=\linewidth]{figures/shared_local_mem.png}
         \caption{The four VMs, blue colered, share the local memory region. It's possible that guest physical address of two VMs end up mapping to the same machine physical address, VM2 and VM3 for example.}
         \label{fig:shared local memory}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{\textwidth}
         \includegraphics[height=.1\textheight,width=\linewidth]{figures/dedicated_local_mem.png}
         \caption{The four VMs, blue colered own its own local memory region. These regions are not shared with other VMs.}
         \label{fig:dedicated local memory}
     \end{subfigure}
     \caption{Configuration of local memory region.}
     \label{fig:local memory architecture}
\end{figure*}

>>>>

\begin{figure*}[h!]
     \centering
     \captionsetup[subfigure]{position=b}
     \begin{subfigure}[b]{0.28\textwidth}
         \centering
         \includegraphics[height=.15\textheight]{figures/monolithic.png}
         \caption{Monolithic architecture, hardware components are bounded within a machine.}
         \label{fig:monolithic architecture}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{0.68\textwidth}
         \centering
         \includegraphics[height=.15\textheight]{figures/disaggregated.png}
         \caption{Disaggregated architecture, hardware components are separate: there are CPU-blade, memory-blade, storage-blade. We also assume there is local memory located with CPU}
         \label{fig:disaggregated architecture}
     \end{subfigure}
     \caption{Monolithic architecture and disaggregated architecture.}
     \label{fig:architecture}
\end{figure*}

% Figure for memory hierarchy
\begin{figure}[h!]
     \centering
     \includegraphics[width=\linewidth,height=.15\textheight]{figures/memory_hierarchy.png}
     \caption{Memory hierarchy of disaggregated architecture.}
     \label{fig:memory hierarchy}
\end{figure}

@@

Also, we assume a hierarchical memory architecture. As shown in  Fig \ref{fig:memory hierarchy}, there are CPU cache, local memory, remote memory, and remote storage. The CPU access latency is shorter as as the layer grows up and the capacity is larger as the layer goes down. The interaction between each layer can only happen with the one's upper or lower layer. Cross-layer interaction is not allowed. Though a flat memory architecture is also a possible design to implement disaggregated architecture, we keep a simple model for better answering our problems.

@@

% Figure of local memory architecture
\begin{figure*}[h!]
     \centering
     \captionsetup[subfigure]{position=b}
     \begin{subfigure}[b]{\textwidth}
         \includegraphics[height=.025\textheight,width=\linewidth]{figures/memory_region.png}
         \caption{Separate physical main memory into local (slash-filled) and remote memory resgions.}
         \label{fig:local memory regions}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{\textwidth}
         \includegraphics[height=.05\textheight,width=\linewidth]{figures/shared_local_mem.png}
         \caption{The four VMs, blue colered, share the local memory region. It's possible that guest physical address of two VMs end up mapping to the same machine physical address, VM2 and VM3 for example.}
         \label{fig:shared local memory}
     \end{subfigure}
     \hfill
     \begin{subfigure}[b]{\textwidth}
         \includegraphics[height=.05\textheight,width=\linewidth]{figures/dedicated_local_mem.png}
         \caption{The four VMs, blue colered own its own local memory region. These regions are not shared with other VMs.}
         \label{fig:dedicated local memory}
     \end{subfigure}
     \caption{Configuration of local memory region.}
     \label{fig:local memory architecture}
\end{figure*}
